%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{ZAMAR}}}}} % First name

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{ROURA}}}}} % Last name

	\vspace{6pt}

	{\huge Data Engineer} % Career or current job title

	% {\huge Software Developer} % Career or current job title


\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Madrid}\\
	\icon{Phone}{12}{+34 652 45 96 46}\\
	\icon{At}{12}{\href{mailto:zamarroura@gmail.com}{zamarroura@gmail.com}}\\
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{https://zamar-roura.com}{zamar-roura.com}}\\
	\icon{Github}{12}{\href{https://github.com/zamar-roura}{github.com/zamar-roura}}\\
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/zamarelahi/}{linkedin.com/zamarelahi}}\\
\end{minipage}

\vspace{1cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{1\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	I am a \textcolor[HTML]{d81e5b}{data engineer}, software developer, and dad joke advocate. I thrive in the search of unexplored insights into common day tasks.
	I like to find clean solutions to problems and am constantly working to improve my knowledge day by day.

\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{0.5cm}
\cvsect{Work Experience}

\begin{entrylist}
	\entry
	{2020 -- today}
	{Data Engineer at Prensa Iberica}
	{Madrid}
	{
	\\{\large Shaped a 1000+ employees news press from subjective culture to data driven}
	\vspace{0.3cm}
	\\- Stream the daily inflow of data to different endpoints. (\textcolor[HTML]{d81e5b}{Airflow, BigQuery, Kafka, Python})
	\\- Built custom client-side A/B Testing solution. (\textcolor[HTML]{d81e5b}{Google Tag Manager})
	\\- Designed \& developed real time analytics. (\textcolor[HTML]{d81e5b}{Apache Druid})
	\\- Data standardization of +30 sites derived from a recent adquisition. (\textcolor[HTML]{d81e5b}{Integrated Datalayer \& CMS})
	\\- Migration of the internal CMP to \textcolor[HTML]{d81e5b}{Piano}, guaranteeing funnel and subscription analytics compabilities.
	\\- Established CI/CD procedures. This way the team has been given more flexibility and security towards new changes and refactoring. (\textcolor[HTML]{d81e5b}{Gitlab, Docker, Rancher})
	}
	\entry
	{2019 -- 2020}
	{Junior Project Enginner at GMV}
	{Madrid}
	{
	\\{\large Satellite Reference Database - METEOSAT Third Generation}
	\vspace{0.3cm}
	\\- Configuration database of telemetry \& telecommand patterns (\textcolor[HTML]{d81e5b}{Oracle SQL})
	\\- Internal version control system for satellite hardware component configurations (\textcolor[HTML]{d81e5b}{Java, Python})
	}
	\entry
	{2017 -- 2019}
	{Junior Consultant at Leda-mc Consulting}
	{Madrid}
	{
	\\{\large Auditing software developed by companies such as IBM, INDRA, NEORIS, EVERIS, ACCENTURE, HUAWEI, NOKIA}
	\vspace{0.3cm}
	\\- Dashboard reports of software economic indicators (\textcolor[HTML]{d81e5b}{Excel, VBA})
	\\- Automated internal operative of the company (\textcolor[HTML]{d81e5b}{Python})
	}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{0.3cm}
\cvsect{Education}

\begin{entrylist}
	\entry
		{2014 -- 2018}
		{B.S in Computer Engineering at Universidad de Alcalá de Henares}
		{}
		{\\Specialized on Data Mining \& Automatic Extractions\\Concentation on Pattern Designs for Object Oriented Programming\\Class representative}
\end{entrylist}


%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.7\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{\href{https://zamar-roura.com/projects}{Personal Projects}}

	\href{https://spotifycloud.zamar-roura.com}{\textcolor{blue}{Spotify Wordcloud}}: Get the most frequent words in the lyrics of any playlist \\
	\href{https://twitter.com/TweetToLlamaBot}{\textcolor{blue}{TweetToLlamaBot}}: Twitter Bot that llamifies any tweet that mentions him \\
	\href{https://www.commondevs.com}{\textcolor{blue}{Common Devs}}: Flutter Mobile App development \\
	\href{https://github.com/zamar-roura/tinder-adventures}{\textcolor{blue}{Tinder Premium APK}}: Tinder APK to obtain premium functionalities \\
	\href{https://zamar-roura.com/projects}{\textcolor{blue}{And more...}}\\
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Languages}

	\textbf{Spanish} - Native\\
	\textbf{English} - Certificate in Advanced English (C1)\\
	\textbf{Hindi/Urdu} - Paternal lineage \\

\end{minipage}



%----------------------------------------------------------------------------------------

\end{document}
